### 2018-06-13 Sections/optimising_the_world.tex
More opt algs

@@

\subsubsection{Other quantum optimisation algorithms}

@@

A quantum-enhanced algorithm for performing least squares fitting\index{Least squares fitting} was described by \cite{HHL?}, potentially offering an exponential enhancement, depending on the sparsity of the data. As input it takes a set of data-points, \mbox{$(x_i,y_i)$}, and functions, $f_j$, outputting a set of coefficients, $\lambda_k$, defining a linear combination of those functions that fits the data, as well as a parameter characterising the quality of the fit. That is, we find the $\lambda$ that defines the fitting function\index{Fitting function},
\begin{align}
f_{\vec\lambda(x)} = \sum_k \lambda_k f_k(x),
\end{align}
such that the quality estimator\index{Quality estimator} is minimised following a sum-of-squares metric,
\begin{align}
E = \sum_i |f_{\vec\lambda}(x_i)-y_i|^2.	
\end{align}
This can be thought of as an optimisation problem in the sense that our goal is to find a linear combination of functions that maximises the fit quality. This problem finds widespread use across many fields, particularly in statistics.

>>>>

We now provide a non-comprehensive overview of some of the better-known quantum optimisation algorithms. The speedups offered by these algorithms vary enormously, from simple quadratic enhancements all the way to exponential enhancement.

@@

\subsubsection{Non-satisfiability-based optimisation algorithms}

@@

A quantum-enhanced algorithm for performing least squares fitting\index{Least squares fitting} was described by \cite{HHL?}, potentially offering exponential enhancement, depending on the sparsity of the data.

As input it takes a set of data-points, \mbox{$(x_i,y_i)$}, and functions, $f_j$, outputting a set of coefficients, $\lambda_k$, defining a linear combination of those functions that fits the data, as well as a parameter characterising the quality of the fit, $E$. That is, we find the $\lambda$ that defines the fitting function\index{Fitting function},
\begin{align}
f_{\vec\lambda(x)} = \sum_k \lambda_k f_k(x),
\end{align}
such that the quality estimator\index{Quality estimator} is minimised according to a sum-of-squares\index{Sum of squares} metric,
\begin{align}
E = \sum_i |f_{\vec\lambda}(x_i)-y_i|^2.	
\end{align}

This can be thought of as an optimisation problem in the sense that our goal is to find a linear combination of functions that maximises the fit quality. This problem finds widespread use across many fields, particularly in statistics where it is ubiquitous.
